\documentclass[11pt]{article}

\pagestyle{empty}

\begin{document}

\begin{center}
\Large \LaTeX\ For Beginner

\small BY

\Large ZAYN KHAN

\large ( Extra Function )
\end{center}


Let's Do Some Extra Function !

If you want to center you letters without mathmode ( double \$\ )

\begin{center}This will shows in center.\end{center} 

You can do this 

 ( $\backslash$begin\{center\} Your words  $\backslash$end\{center\} )
 
 Or This
 
 ( $\backslash$begin\{center\}
 
  Your words 
  
   $\backslash$end\{center\} )

\vspace{1cm}

If you want to align right then

\begin{flushright}
This will show on right
\end{flushright}

\vspace{1cm}

Or if you want to left align then

\begin{flushleft}
This will show on left
\end{flushleft}

Recipe 

( $\backslash$begin\{flushright\}

  Your words here

  $\backslash$end\{flushright\} )
  
  For left just change ( flushright ) to ( flushleft )
  
\vspace{1cm}

If you want to make Text bigger or smaller then do this like :

\begin{enumerate}

\item \tiny{This is called (tiny)}
\item \scriptsize{This is called (scriptsize)}
\item \small{This is called (small)}
\item \normalsize{This is called (normalsize)}
\item \large{This is called (large)}
\item \Large{This is called (Large)}
\item \LARGE{This is called (LARGE)}
\item \huge{This is called (huge)}

\end{enumerate}  
  
  
  \vspace{1cm}  
  
  I use enumerate just for better explain you don't need to use
  
  enumerate while writing an actual document for example like :
  
  \huge{This is called (huge)}

Recipe :

There are two ways to do like this

1. $\backslash$which size you want \{words\}

(e.g. $\backslash$Large\{This is called(Large)\}

\vspace{1cm}

\normalsize Something is wrong right ? From before recipe to e.g everything is in 

huge size but why ? And why not from 7.(huge) ?

The answer is the 7.(huge is inside the enumerate which have begin and

end point that's why that don't flow up to the next documents and

before recipe (huge) we don't have any begin or close point also

i am writing this question and answer using $\backslash$normalsize

\vspace{1cm}

Then why i show this? And is there any help to stop them from flow?

The answer is i show you for save your time and yeah there is way for

stop flow over the next documents. Here is it:

\vspace{1cm}

{\large This is called (large)}

\vspace{1cm}

see now this isn't flow this time. Here is the recipe:

\{$\backslash$large your words\}  . This is just about \{\} and knowledge.

Remember : between $\backslash$and large there is no space but after 

$\backslash$large there need a space like \{$\backslash$large your words\}

\vspace{1cm}

{\large 2.}

So here is the way no. 2

\begin{tiny}
This is called tiny
\end{tiny}

\begin{scriptsize}
This is called scriptsize
\end{scriptsize}

\begin{small}
This is called small
\end{small}

\begin{normalsize}
This is called normal size
\end{normalsize}

\begin{large}
This is called large
\end{large}

\begin{Large}
This is called large
\end{Large}

\begin{LARGE}
This is called LARGE
\end{LARGE}

\begin{huge}
This is called huge
\end{huge}

Recipe :

$\backslash$begin\{your size\}

your words

$\backslash$end\{your size\}

(e.g.)

$\backslash$begin\{large\}

your words

$\backslash$end\{large\}

\vspace{1cm}

End of the day we found 3 ways to do size filtering :

1. enumerate

2. $\backslash$size

3. using begin $\backslash$size 

Remember : enumerate gives you next line automatically but if you using

$\backslash$size or begin $\backslash$size they don't give you you need to

do that by your own.

\vspace{1cm}

enumerate is good for line up while you are learning this can help you

to learn two things in once. You can also use itemize or custom.

\vspace{1cm}

$\backslash$size can help you for time saving when you are in hurry and

this looks cool for me. But use the \{\} begin size and after words for

stop flow.

$\backslash$begin can help for use and located individual 

and looks so rich
also mess up code. This can take your extra time.

\vspace{1cm}

Ok ! Let's try them 4 :

\begin{enumerate}
\item \large{This is written in enumerate}
\end{enumerate}

\large This is written in $\backslash$large without \{\}

\begin{large}
This is written in $\backslash$begin size
\end{large}

{\large This is written in $\backslash$large with \{\} both start and end }

\vspace{1cm}

If you want to make big or small just one word in a sentence then 

do like this :

This is  {\tiny (tiny)} and {\normalsize(normalsize)} or {\huge(huge)}

Recipe write in one line :

This is \{$\backslash$tiny (tiny)\} and 

\{$\backslash$normalsize (normalsize)\}

or \{$\backslash$huge (huge)\}

\vspace{1cm}

\end{document}