\documentclass[12pt]{article}
\pagestyle{empty}
\usepackage[margin=1cm]{geometry}

\begin{document}
\begin{center}
\Large \LaTeX\ For Beginner

\small BY

\Large ZAYN KHAN :)

\large ( Page margin )
\end{center}

So this page contain some information about page setup/margin so let's go :::

\vspace{0.5cm}

So as you can see i setup margin of this page 1cm from every side.

I mean ( from top to bottom , right to left ). Here how i do this :::

\vspace{0.5cm}

Before begin document and after document class we need to load a package

with some attributes ( $\backslash$usepackage[margin=1cm]\{geometry\} )

So that will do everything about margin i use this now cuz it's quite simple in one words. Otherwise need

more customize package load more specific like if you want to give margin different from everyside like :::

\vspace{0.5cm}

From bottom you want 0.5cm , top 1cm , right 0.6cm , left 2cm. You can also use in for inch.

\vspace{0.5cm}

Do this :::

$\backslash$usepackage[top=1cm, bottom=0.5cm, right=0.6cm, left-2cm]
\{geometry\}

\vspace{0.5cm}

Some paper you can load :::

a0paper, a1paper, a2paper, a3paper, a4paper, a5paper, a6paper,b0paper, b1paper, b2paper, b3paper,

 b4paper, b5paper, b6paper,c0paper, c1paper, c2paper, c3paper, c4paper, c5paper, c6paper,b0j, b1j,
 
  b2j, b3j, b4j, b5j, b6j,ansiapaper, ansibpaper, ansicpaper, ansidpaper, ansiepaper,letterpaper,
  
   executivepaper, legalpaper

\vspace{0.5cm}

You can set you output paper to landscape with geometry command like this :::

$\backslash$usepackage\{geometry\}
$\backslash$geometry\{a4paper, landscape, margin=2in\}

\vspace{0.5cm}

Remember :::

\vspace{0.5cm}

1. LaTeX's margins are, by default, 1.5 inches wide on 12pt 

documents, 1.75 inches wide on 11pt documents,
and 1.875 inches wide on 10pt documents.
 
 
2. If you want to give space between words but not line space then just press spacebar is not enough

for \LaTeX\ you need to give $\backslash$,(comma) for one letter of space.


3 .If you want to write \LaTeX\ This way then do this ( $\backslash$LaTeX$\backslash$ ) second $\backslash$ for one letter of space.

 Don't try this on another other words insted \TeX\ TeX and \LaTeX\ LaTeX and be sure about spelling.

4. Avoid () Those are just for better explanation.

5. I use $\backslash$pagestyle{empty} on top after document class for prevent printing page

number on every page on bottom i don't like that on my document avoid this command if

you writing a book or want page number by default \LaTeX\ use page number.

6. For more \TeX\ or \LaTeX\ commands, method use webpage online.


\begin{center}
\Huge Thank you
\end{center}
\end{document}